---
layout: review, 11pt
linenumbers: true
title: "R clients for working with scholarly metadata and full text"
author:
  - name: Scott Chamberlain
    affiliation: cstar
    email: scott(at)ropensci.org
    footnote: Corresponding author
address:
  - code: cstar
    address: |
      University of California, Berkeley, CA, USA
abstract: |
      1. xxx

      2. xxx

      3. xxx

      4. xxxx

bibliography: components/references.bib
csl: components/peerj.csl
documentclass: components/elsarticle

output:
  pdf_document:
    template: components/elsarticle.latex
    keep_tex: true
    fig_caption: true
---


```{r compile-settings, include=FALSE}
library("methods")
library("knitr")
opts_chunk$set(
  tidy = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = 1,
  comment = '#>',
  collapse = TRUE,
  verbose = TRUE
)
basename <- gsub(".Rmd", "", knitr:::knit_concord$get('infile'))
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
```

# Introduction

xxxx

```{r echo=FALSE, results='hide', eval=FALSE}
install.packages("fulltext", dependencies=TRUE)
```

```{r echo=FALSE, results='hide'}
library("fulltext")
```

# The packages

xxx

## Package interface

xxx

### fulltext

### rentrez

### rplos

### rcrossref

# Conclusions and future directions

* pt 1
* pt 2
* pt 3
* pt 4

# Acknowledgements

This project was supported in part by the Alfred P Sloan
Foundation (Grant 2013-6-22).

# Data Accessibility

All scripts and data used in this paper can be found in the permanent
data archive Zenodo under the digital object identifier (DOI). This DOI corresponds to a snapshot of the GitHub repository at [github.com/sckott/mstext](https://github.com/sckott/mstext). Software can be found at [github.com/ropensci/fulltext](https://github.com/ropensci/fulltext), under the open and permissive MIT license.

# References

[mit]: http://choosealicense.com/licenses/mit/
